Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Add NOV table

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    for (cs in names(io$accra$outcomes$whw)){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$whw)), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

>>>>

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    for (cs in names(io$accra$outcomes$whw)[1]){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$whw)), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

No Other Vehicle matrix for baseline for each case study

### No Other Vehicle matrix matrix for baseline {#nov_baseline}

```{r nov}

for(city in cities){
  if (!city %in% c('bogota', 'vizag')){
    for (cs in names(io$accra$outcomes$whw)[1]){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$nov)), caption = paste('NOV ', cs, ' matrix for ', city)))
      cat("\n")
    }
